
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Without doubt, the three years of my PhD were an amazing time.

For that, I first want to thank my adviser Tilman Plehn: for taking me
on as a student, for working with me on interesting physics, and for
disagreeing with me on countless questions over coffee. I am sincerely
grateful to him for always having my back. This includes him coming
into the office on a Sunday morning to get me a backup laptop when
mine broke down days before a deadline. His support is also, I
suspect, responsible for the postdoc offers I got.
%
% and, I suspect, some severe
% pulling of strings to make sure I got postdoc offers.
%
% And last but certainly not least, I am grateful to him for clearing
% the way to an academic career for me, even though I finally decided
% against this path.

I would like to thank Bj\"orn Malte Sch\"afer for reading and
refereeing this thesis, and Monica Dunford and Wolfgang Schlegel for
completing my examination committee. Further praise is reserved until
after the defence.

The Research Training Group `Particle physics at the LHC' (DFG GRK
1940) paid my salary and, together with the Heidelberg Graduate School
of Fundamental Physics, my travels. I am grateful for their support.

During the different PhD projects, I had the great pleasure to
collaborate with a number of amazing scientists. Ayres Freitas and
David L\'opez-Val saw me off to a great start and taught me a
lot. Anke Biek\"otter joined us a little later, giving fresh impetus
to our research. Chasing the diboson ambulance with JoAnne Hewett,
Joachim Kopp, Tom Rizzo, and Jamie Tattersall was a wild and fun
ride. But one of the best ideas during my PhD was to grab a beer with
Kyle Cranmer in Caf\'e Botanik. Working with him was inspiring, and
was even more fun once Felix Kling joined our team.

The work presented in this thesis benefitted greatly from discussions
with others. In particular I would like to express my gratitude to
Anja Butter for keeping me on track with sharp questions, Juan
Gonzalez-Fraile for teaching me one thing or two about effective field
theories, Peter Schichtel for helping me set up and use
\toolfont{MadMax}, and Torben Schell, who is an unwavering source of
physics knowledge as well as a saviour in the hour of incomprehensible
linker errors.

From Marstall lunches to Pheno `class trips', with nut cakes, PhD
hats, and the eternal coffee list, the Heidelberg pheno group was akin
to a second home in the last three years. I would like to thank Martin
Bauer, Anke, Katja B\"ohnke, Anja, Nishita Desai, Karin Firnkes, Josua
G\"ocking, Juan, Jamil Hetzel, Sebastian Hoof, Jan Horak, Thomas
Hugle, J\"org J\"ackel, Florian Jetter, Martin Klassen, Lara Kuhn,
Rabea Link, Viraf Mehta, Luminita Mihaila, Rhea Moutafis, Tilman,
Peter Reimitz, Michael Russel, Torben Schell, Sebastian Schenk, Peter
Schichtel, Linda Shen, Beatriz Tapia Oregui, Jamie Tattersall,
Valentin Tenorth, Jennifer Thompson, Susanne Westhoff, and Nikolai
Zerf. I am grateful to Anke, Patrick, and Sebastian for the awesome
wine\,\&\,cheese seminar. Most of all, I would like to thank Anja and
Torben, who shared nearly the entire PhD journey with me. Without the
two, these three years would not have been half as much fun.

\blackout{Further away from the Philosophenweg, I would like to thank
  the friends whose company I enjoyed during the last years, and in
  particular give a shout out to the Dossenheim gang, Marcel Gutsche,
  Clemens Hassel, and Julia Velte, and to Christina Eilers. I would
  like to especially thank Astrid Hiller Blin, who jump-started my
  days over coffee and arXiv no matter the distance. A big thank you
  goes to my marvellous parents Antje and Andreas Brehmer. And then
  there is Merle Reinhart, who I cannot thank enough and who in just
  about any circumstances makes life better}.

% Further away from the Philosophenweg, I would like to thank the
% friends whose company I enjoyed during the last years, and in
% particular give a shout out to the Dossenheim gang\,---\,Marcel
% Gutsche, Clemens Hassel, and Julia Velte\,---\,and to Christina
% Eilers. I would like to especially thank Astrid Hiller Blin, who
% jump-started many of my days over coffee and arXiv. A big thank you
% goes to my marvellous parents Antje and Andreas Brehmer. And then
% there is Merle Reinhart, who I cannot thank enough and who in just
% about any circumstances makes life better.

If this thesis is legible, it is largely because of the trustworthy
proof readers. A big thanks to Anja, Anke, Eric Miller, Juan, Martin
Bauer, Nikolai, Patrick, and Sebastian.\comment{Add Clemens, Marcel,
  Juli, Christina, if they provide any feedback.} In particular, I am
indebted to Antje, Astrid, and Merle, who were crazy enough to read
the whole thing from front to end.

To all these people, a heartfelt thank you.
