
% \setchapterpreamble[ur]{%
% \dictum[W.~Allen~\cite{allen1971getting}]{%
% Can we actually know the universe? My God, it’s hard enough finding your way around in Chinatown.}%
% \vspace*{2cm}}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusions}
\label{chapter:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\firstword{M}{easuring the properties} of the Higgs boson is one of
the most important missions for Run~2 of the LHC and may help us
understand some of the open questions of fundamental physics. The
efficient combination of different experimental channels and their
interpretation in the many theories of physics beyond the Standard Model
benefit from a universal parametrisation of these properties. The
dimension-six operators of linear Higgs effective field theory provide
such a framework that is theoretically well-motivated, largely
independent of model assumptions, and phenomenologically powerful.

In this thesis we discussed two aspects of this approach, both of
immediate practical relevance: we analysed whether these effective
operators accurately capture the relevant signatures of specific
scenarios of new physics, and we developed statistical tools that can
help to design efficient measurements of the Higgs properties.

\newparagraph
%
In the first part we argued that the validity of the dimension-six
model for LHC Higgs physics is not at all obvious. The
effective field theory approach is based on the assumption that the
typical mass scale of new physics is significantly larger than the
experimentally probed energy scale. But the limited precision of Higgs
measurements at the LHC cannot guarantee such a scale separation:
signatures of weakly coupled new physics can only have a relevant size
if the new physics scale is close to the electroweak scale, and the
effective theory may not be valid in general.

We studied whether the dimension-six model is nevertheless useful for
Higgs signatures
%as a parametrisation of new physics signatures
by comparing the phenomenology of different scenarios of physics
beyond the Standard Model to the corresponding effective theories. For
extended Higgs sectors with an additional scalar singlet or doublet,
scalar top partners, and heavy vector bosons, we analysed total rates
and kinematic distributions in the most important Higgs production and
decay channels.

Our results show that the agreement between the full models and their
dimension-six approximations crucially depends on the matching
procedure, \ie the construction of the effective theory from a full
model. Standard procedures for the matching, defined in the unbroken
phase of the electroweak symmetry, lead to large errors of the
effective field theory description already for total rates, which only
deteriorate in kinematic distributions.

This does not mean, though, that the dimension-six model is not useful
for Higgs physics. We introduced $v$-improved matching, a procedure
that improves the performance of the dimension-six model by resumming
certain terms that arise during electroweak symmetry breaking. While
formally of subleading order in the EFT expansion, these effects can
be large under LHC conditions. With such a matching, the dimension-six
model provides a good description even in many scenarios where the EFT
validity is not self-evident, and typically only breaks down at new
resonances or in the far high-energy tails of certain distributions.

In addition, we discussed the role of squared amplitudes from
dimension-six operators. Even though they appear at the same order in
the EFT expansion as the leading effects from the neglected
dimension-eight operators, we argued that it is often preferable to
include them in calculations. In a detailed study of Higgs production
in weak boson fusion, we finally showed that the transverse momenta of
the tagging jets provide the best measure of the unobservable momentum
transfer.

Our research was motivated by the question which parametrisation of
Higgs properties to use during Run~2 of the LHC. With these results we
conclude that despite the unclear scale separation, the dimension-six
operators of linear Higgs effective field theory capture a wide range
of new physics signatures accurately. Subtleties in the matching
procedure are not a problem for an experimental fit of dimension-six
operators at the LHC, but have to be taken into account when
interpreting the results in specific models.

\newparagraph
%
Having established that Higgs EFT works well as a largely
model-independent language for Higgs physics at the LHC, we turned to
the question how its parameters can be measured most efficiently. The
high-dimensional theory space defined by the Higgs properties and the
intricate kinematics of some Higgs channels present challenges for
traditional analysis methods based on cuts and kinematic
distributions, while modern multivariate methods can be
non-transparent and difficult to reproduce.

We showed that information geometry allows us to understand the
information contained in LHC signatures and can help optimise
measurement strategies. This formalism is based on the Fisher
information matrix, which according to the Cram\'er-Rao bound
quantifies the maximal precision with which continuous model
parameters can be measured in an experiment. It can be interpreted
geometrically, and its properties are well-suited to high-dimensional
parameter spaces such as that of Higgs effective field theory.

We developed a novel algorithm to calculate the Fisher information in
LHC processes, taking into account the full kinematics including all
correlations. In addition to the total Fisher information, we also
showed how to calculate the distribution of the differential
information over phase space, and the information in individual
kinematic distributions. These tools define the important phase-space
regions and observables for an analysis and let us compare the
discrimination power of traditional histogram-based analyses to that
of modern multivariate ones.

Applying these techniques to Higgs production in weak boson fusion
with decays into tau pairs or four leptons, we demonstrated that the
kinematics of the tagging jets is significantly more sensitive to new
physics in the form of dimension-six operators than observables that
characterise the Higgs decay.  The transverse momenta of these jets
and their angular correlations are particularly powerful
observables. Still, a multivariate analysis with matrix-element-based
methods or machine-learning tools can potentially extract
significantly more information. Finally, we analysed the structure of
Higgs production with a single top. Higgs decay products and angular
distributions between the Higgs and top daughters are sensitive to
different operators, but overall the sensitivity of this process to
dimension-six physics is limited.

% This is the first application of information geometry to high-energy
% physics.
%
While there is no shortage of statistical tools in the field, these
new methods can help to plan and optimise measurements of
high-dimensional, continuous parameter spaces in an intuitive way.  We
demonstrated this approach in different Higgs channels for
dimension-six operators, showing how it aids efficient measurements of
Higgs properties and thus contributes to the second question raised in
the introduction. But our tools can easily be translated to other
processes and models.

\newparagraph
%
To summarise, effective dimension-six operators provide a powerful
framework to measure and understand the properties of the Higgs
boson. We analysed the validity of this approach at the LHC and showed
how it can be improved with a suitable matching procedure. In a next
step, we developed statistical tools based on information geometry to
guide the design of efficient measurement strategies. These new ideas
can contribute to a better understanding of the nature of the Higgs
boson, which may ultimately point us to what lies beyond the Standard
Model.
